Gap formation and stability in non-isothermal protoplanetary discs

### 2014-07-27 paper/model.tex
brief notes on what information should be included
updated paper

\section{Disc-planet models}\label{model}
The system is a two-dimensional, self-gravitating gas disc of mass
$M_d$ rotating about a central star of mass $M_*$. Cylindrical
co-ordinates $(r,\phi,z)$ centred on the star is adopted. The frame is   
non-rotating. Computational units are such that
$G=M_*=\mathcal{R}=\mu=1$ where $G$ is the gravitational constant,
$\mathcal{R}$ is the gas constant and $\mu$ is the mean molecular
weight. %% \cite{lin12}

The disc is governed by the standard fluid equations  
\begin{align}\label{3d_gov_eq}
  &\frac{\p\Sigma}{\p t}+\nabla\cdot(\Sigma \bv)=0, \\
  & \frac{\p\bv}{\p t}+\bv\cdot\nabla\bv= -\frac{1}{\rho}\nabla p 
  - \nabla{\Phi} + \bm{f}_\nu,\\
  & \frac{\p e}{\p t} + \nabla\cdot(e\bv) = -p\nabla\cdot\bv +
  \mathcal{H} - \mathcal{C}, \\
  &\nabla^2\Phi_d = 4\pi G \Sigma \delta(z),\label{poisson}
\end{align}
where $\Sigma$ is the surface density, $\bv = (v_r,v_\phi)$ the fluid
velocity, $p$ is the pressure, $e=p/(\gamma-1)$ is the energy
density and the adiabatic index $\gamma=1.4$ is assumed constant.

The total potential $\Phi$ includes the stellar potential, planet potential
(described below), and the disc potential $\Phi_d$ which satisfies the
Poisson equation \ref{poisson}. Indirect potentials are also included
to account for the non-inertial reference frame. In the momentum
equations, $\bm{f}_\nu$ represent viscous forces whose magnitude is 
characterised by a constant kinematic viscosity parameter $\nu$.

@@

\subsection{Disc model and initial condition}
The disc occupies $r\in[r_\mathrm{in}, r_\mathrm{out}]$ with $\rout =
25\rin$ and $\phi\in[0,2\pi]$. The initial disc is axisymmetric with
surface density profile

\begin{align}\label{initial_density}
   \Sigma_i(r) = \Sigma_0\left(\frac{r}{r_\mathrm{in}}\right)^{-s}
    \left[1 - \sqrt{\frac{r_\mathrm{in}}{r + H_i(\rin)}}\,\right] 
\end{align}
where the power-law index $s=3/2$, $H(r) = \ciso\Omega_k $ defines the disc scale-height 
where $\ciso=\sqrt{p/\Sigma}$ isothermal sound-speed. The disc aspect-ratio is defined as $h\equiv H/r$ and initially
$h_i=0.05$. The surface density scale $\Sigma_0$ is set by  
\begin{align}
\Sigma_0 = \frac{h_i\rout\Omega_k^2(\rout)}{\pi G Q_o},
\end{align}
where $Q_o$ is the thin-disc Keplerian Toomre parameter at the outer boundary initially.

@@

\subsection{Planet potential}\label{planet_config}
The planet potential is given by
\begin{align}
\Phi_p = -\frac{GM_p}{\sqrt{|\bm{r} - \bm{r}_p|^2 + \epsilon_p^2}},
\end{align}
where $M_p=qM_*$ is the planet mass ($q$ is the planet-to-star mass ratio), $\bm{r}_p=(r_p,\phi_p)$ is the planet's 
position in the disc and $\epsilon_p=0.5r_h$ is a softening length with $r_h=(q/3)^{1/3}r_p$ being the Hill radius. 
%Hill radius chosen so eps doesn't change with time (scale-height does)
In most simulations the planet is held on a fixed circular orbit, so that $r_p(t) = r_p(0) \equiv r_{p0}$. This also
defines the time unit $P_0\equiv 2\pi/\Omega_k(r_{p0})$ used to describe results.

In this study only one planet mass is considered, with $q=10^{-3}$. This corresponds to a Jupiter-mass
planet if $M_*=M_{\sun}$. The initial orbital radius is $r_{p0} = 10\rin$.

\section{Numerical experiments}\label{method}
The self-gravitating disc-planet system is evolved using the 
\texttt{FARGO-ADSG} code \citep{baruteau08, baruteau08b}. This is a modified version 
of the original \texttt{FARGO} code \citep{masset00a} to include the energy 
equation and disc gravity. The code employs finite-difference scheme similar 
to the \texttt{ZEUS} code \citep{stone92}, but with a modified azimuthal transport 
algorithm to circumvent the time-step restriction set by the inner disc boundary. 
The disc is divided into $(N_r,N_\phi)$ zones in the radial and azimuthal directions, 
respectively. The grid spacing is logarithmic in radius and uniform in azimuth.

\subsection{Control parameters}
The disc parameters are $Q_o$, which characterizes the strength of self-gravity; 
and $\beta$ which sets the cooling time. Two levels of self-gravity is considered: 
a light disc with $Q_o=8$ and a heavy disc with $Q_o=1.5$. The cooling 
parameter $\beta$ is chosen indirectly  through the parameter
$\tilde{\beta}$ such that

@@

\subsection{Simulation procedure}
The disc is evolved without a planet for $t\in[0,20]P_0$. The planet potential is smoothly switched on
between $t\in[20,30]P_0$.
%%  In a separate set of calculations the planet
%% potential is turned off after $t>t_\mathrm{off}$, immediately  
%% afterwhich the surface density, energy density and velocity fields are
%% azimuthally averaged and then subject to random surface density  
%% perturbations of magnitude $10^{-2}$.

\subsection{Diagonistic measures}
%% According to previous 2D studies, the key quantitiy in describing the
%% stability of radially structured non-barotropic discs is the
%% \emph{generalized vortensity} (GV): 
%% \begin{align}
%%   \tilde{\eta}\equiv \left(\frac{\kappa^2}{2\Omega\Sigma}\right)S^{-2/\gamma}, 
%% \end{align}
%% where $S \equiv p/\Sigma^\gamma$ is defined to be the entropy. The
%% quantity in brackets, $\eta\equiv \kappa^2/2\Omega\Sigma$, is the
%% usual vortensity or potential vorticity (PV).

>>>>

\section{Disc-planet models}\label{model}
The system is a two-dimensional non-self-gravitating gas disc orbiting
a central star of mass $M_*$.  
%self-gravitating gas disc of mass
%$M_d$ rotating about a central star of mass $M_*$. 
Cylindrical
co-ordinates $(r,\phi,z)$ centred on the star is adopted. The frame is   
non-rotating. Computational units are such that 
$G=M_*=\mathcal{R}=\mu=1$ where $G$ is the gravitational constant,
$\mathcal{R}$ is the gas constant and $\mu$ is the mean molecular
weight. %% \cite{lin12}

The disc is governed by the standard fluid equations  
\begin{align}\label{3d_gov_eq}
  &\frac{\p\Sigma}{\p t}+\nabla\cdot(\Sigma \bv)=0, \\
  & \frac{\p\bv}{\p t}+\bv\cdot\nabla\bv= -\frac{1}{\rho}\nabla p 
  - \nabla{\Phi} + \bm{f}_\nu,\\
  & \frac{\p e}{\p t} + \nabla\cdot(e\bv) = -p\nabla\cdot\bv +
  \mathcal{H} - \mathcal{C}, %\\
%  &\nabla^2\Phi_d = 4\pi G \Sigma \delta(z),\label{poisson}
\end{align}
where $\Sigma$ is the surface density, $\bv = (v_r,v_\phi)$ the fluid
velocity, $p$ is the pressure, $e=p/(\gamma-1)$ is the energy
density and the adiabatic index $\gamma=1.4$ is assumed constant.

The total potential $\Phi$ includes the stellar potential, planet potential
(described below)%, and the disc potential $\Phi_d$ which satisfies the
%Poisson equation \ref{poisson}. 
and indirect potentials are also included
to account for the non-inertial reference frame. In the momentum
equations, $\bm{f}_\nu$ represent viscous forces whose magnitude is 
characterised by a constant kinematic viscosity parameter
$\nu$. However, we will be considering effectively inviscid discs by
adopting small values of $\nu$ .

@@

\subsection{Disc model and initial condition}
The disc occupies $r\in[r_\mathrm{in}, r_\mathrm{out}]$ with $\rout =
40\rin$ and $\phi\in[0,2\pi]$. The initial disc is axisymmetric with
surface density profile

\begin{align}\label{initial_density}
   \Sigma_i(r) = \Sigma_0\left(\frac{r}{r_\mathrm{in}}\right)^{-s}
    \left[1 - \sqrt{\frac{r_\mathrm{in}}{r + H_i(\rin)}}\,\right] 
\end{align}
where the power-law index $s=2$, $H(r) = \ciso\Omega_k $ defines the disc scale-height 
where $\ciso=\sqrt{p/\Sigma}$ isothermal sound-speed. The disc aspect-ratio is defined as $h\equiv H/r$ and initially
$h=0.05$. For a non-self-gravitating disc, the surface density scale
$\Sigma_0$ is arbitrary.

%The surface density scale $\Sigma_0$ is set by  
%\begin{align}
%\Sigma_0 = \frac{h_i\rout\Omega_k^2(\rout)}{\pi G Q_o},
%\end{align}
%where $Q_o$ is the thin-disc Keplerian Toomre parameter at the outer boundary initially.

@@

\subsection{Planet potential}\label{planet_config}
The planet potential is given by 
\begin{align}
\Phi_p = -\frac{GM_p}{\sqrt{|\bm{r} - \bm{r}_p|^2 + \epsilon_p^2}},
\end{align}
where $M_p$ is the planet mass and we fix $q\equiv M_p/M_*=10^{-3}$
throughout this work. This corresponds to a Jupiter-mass planet if $M_*=M_{\sun}$. 
The planet's position in the disc 
 $\bm{r}_p=(r_p,\phi_p)$  and $\epsilon_p=0.5r_h$ is a softening
length with $r_h=(q/3)^{1/3}r_p$ being the Hill radius.  
%Hill radius chosen so eps doesn't change with time (scale-height does)
The planet is held on a fixed circular orbit with $ r_p = 10\rin$. This also
defines the time unit $P_0\equiv 2\pi/\Omega_k(r_p)$ used to describe results. 
%In this study only one planet mass is considered, with $q=10^{-3}$. 
%The initial orbital radius is

\section{Numerical experiments}\label{method}
The self-gravitating disc-planet system is evolved using the 
\texttt{FARGO-ADSG} code \citep{baruteau08, baruteau08b}. This is a modified version 
of the original \texttt{FARGO} code \citep{masset00a} to include the energy 
equation. The code employs finite-difference scheme similar 
to the \texttt{ZEUS} code \citep{stone92}, but with a modified azimuthal transport 
algorithm to circumvent the time-step restriction set by the inner disc boundary. 
The disc is divided into $(N_r,N_\phi)$ zones in the radial and azimuthal directions, 
respectively. The grid spacing is logarithmic in radius and uniform in azimuth.

\subsection{Parametrized cooling}
In this work we only vary one control parameter: the cooling
time. 
%The disc parameters are $Q_o$, which characterizes the strength of self-gravity; 
%and $\beta$ which sets the cooling time. Two levels of self-gravity is considered: 
%a light disc with $Q_o=8$ and a heavy disc with $Q_o=1.5$. 
The cooling parameter $\beta$ is chosen indirectly  through the parameter
$\tilde{\beta}$ such that

@@

%\subsection{Simulation procedure}
%The disc is evolved without a planet for $t\in[0,20]P_0$. The planet potential is smoothly switched on
%between $t\in[20,30]P_0$.
%%  In a separate set of calculations the planet
%% potential is turned off after $t>t_\mathrm{off}$, immediately  
%% afterwhich the surface density, energy density and velocity fields are
%% azimuthally averaged and then subject to random surface density  
%% perturbations of magnitude $10^{-2}$.

\subsection{Diagonistic measures}

\subsubsection{Generalized potential vorticity}

The generalized potential vorticity (PV, or vortensity) is defined as
\begin{align}
  \tilde{\eta} = \frac{\kappa^2}{2\Omega\Sigma}\times S^{-2/\gamma}, 
\end{align}
where $\kappa^2 = r^{-3}\partial_r(r^4\Omega^2)$ is the square of the
epicycle frequency, $\Omega=v_\phi/r$ is the angular speed, and
$S\equiv p/\Sigma^\gamma$ is the entropy. The first factor is the
usual potential vorticity.

The generalized PV appears in the description of the linear stability
of radially-structured adiabatic discs \citep{lovelace99,li00}, where
the authors show an extremum in $\teta$ may lead to a dynamical
instability. In a barotropic disc, the entropy factor is absent
and the important quantity is the PV.

\subsubsection{Fourier modes}

\subsubsection{Rossby number}

%{\bf {MKL.} describe vortensity and generalized vortensity, and its
%  relevance to stability. fourier mode amplitude definition and how
%  growth rates are obtained. rossby number. density
%  perturbations. (see lin 2014)
%}

%% According to previous 2D studies, the key quantitiy in describing the
%% stability of radially structured non-barotropic discs is the
%% \emph{generalized vortensity} (GV): 
%% \begin{align}
%%   \tilde{\eta}\equiv \left(\frac{\kappa^2}{2\Omega\Sigma}\right)S^{-2/\gamma}, 
%% \end{align}
%% where $S \equiv p/\Sigma^\gamma$ is defined to be the entropy. The
%% quantity in brackets, $\eta\equiv \kappa^2/2\Omega\Sigma$, is the
%% usual vortensity or potential vorticity (PV).

### 2014-07-27 paper/paper.tex
tex updates
updated paper

\newcommand{\p}{\partial}
\newcommand{\mnras}{MNRAS}
\newcommand{\apj}{ApJ}
\newcommand{\aap}{A\&A}
\newcommand{\apjl}{ApJL}
\newcommand{\araa}{ARAA}
\newcommand{\dd}{\delta}
\newcommand{\adot}{\dot{a}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\gtrsim}{\;\raisebox{-.8ex}{$\buildrel{\textstyle>}\over\sim$}\;}
\newcommand{\lesssim}{\; \raisebox{-.8ex}{$\buildrel{\textstyle<}\over\sim$}\;}
\newcommand{\anrev}{{\it ARA\&A, }}
\newcommand{\apjs}{{\it ApJS, }}
\newcommand{\icar}{{\it Icarus, }}
\newcommand{\mnr}{{\it MNRAS, }}
\newcommand{\nat}{{\it Nature, }}
\newcommand{\sci}{{\it Sci, }}
\newcommand{\ana}{{\it A\&A, }}
\newcommand{\anas}{{\it A\&AS, }}
\newcommand{\aaps}{{\it A\&AS, }}
\newcommand{\anar}{{\it A\&AR, }}
\newcommand{\prd}{{\it Phys. Rev. D }}
\newcommand{\qjl}{{\it QJRAS, }}
\newcommand{\sbar}{\bar{\sigma}}
\newcommand{\avg}[1]{\langle #1 \rangle_\phi}
\newcommand{\bu}{\bm{u}}
\newcommand{\lmax}{l_\mathrm{max}}
\newcommand{\mmax}{m_\mathrm{max}}
\newcommand{\trel}{t_\mathrm{rel}}
\newcommand{\zeus}{{\tt ZEUS-MP }}
\newcommand{\ii}{\mathrm{i}}
\newcommand{\bv}{\bm{v}}
\newcommand{\rin}{r_\mathrm{in}}
\newcommand{\rout}{r_\mathrm{out}}
\newcommand{\ciso}{c_\mathrm{iso}}
\newcommand{\tbeta}{\tilde{\beta}}
\DeclareMathOperator{\erf}{erf}

\title[Gaps in non-isothermal discs]{Gap formation and stability in 
  non-isothermal self-gravitating discs}

\author[Lin]{ Min-Kai Lin
  \thanks{E-mail: mklin924@cita.utoronto.ca} \\ 
Canadian Institute for Theoretical Astrophysics,  
60 St. George Street, Toronto, ON, M5S 3H8, Canada \\
}

@@

\maketitle
\begin{abstract}
Hydrodynamic simulations of self-gravitating disc-planet interactions are presented. The energy equation is solved with a simple cooling law 
such that $\beta = t_c\Omega_k$ is constant, where $t_c$ is the cooling time and $\Omega_k$ is the Keplerian frequency. 
The simulations are customized to examine the stability of gaps opened by massive planets as a function of $\beta$.

>>>>

\newcommand{\p}{\partial}
\newcommand{\mnras}{MNRAS}
\newcommand{\apj}{ApJ}
\newcommand{\aap}{A\&A}
\newcommand{\apjl}{ApJL}
\newcommand{\araa}{ARAA}
\newcommand{\dd}{\delta}
\newcommand{\adot}{\dot{a}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\gtrsim}{\;\raisebox{-.8ex}{$\buildrel{\textstyle>}\over\sim$}\;}
\newcommand{\lesssim}{\; \raisebox{-.8ex}{$\buildrel{\textstyle<}\over\sim$}\;}
\newcommand{\anrev}{{\it ARA\&A, }}
\newcommand{\apjs}{{\it ApJS, }}
\newcommand{\icar}{{\it Icarus, }}
\newcommand{\mnr}{{\it MNRAS, }}
\newcommand{\nat}{{\it Nature, }}
\newcommand{\sci}{{\it Sci, }}
\newcommand{\ana}{{\it A\&A, }}
\newcommand{\anas}{{\it A\&AS, }}
\newcommand{\aaps}{{\it A\&AS, }}
\newcommand{\anar}{{\it A\&AR, }}
\newcommand{\prd}{{\it Phys. Rev. D }}
\newcommand{\qjl}{{\it QJRAS, }}
\newcommand{\sbar}{\bar{\sigma}}
\newcommand{\avg}[1]{\langle #1 \rangle_\phi}
\newcommand{\bu}{\bm{u}}
\newcommand{\lmax}{l_\mathrm{max}}
\newcommand{\mmax}{m_\mathrm{max}}
\newcommand{\trel}{t_\mathrm{rel}}
\newcommand{\zeus}{{\tt ZEUS-MP }}
\newcommand{\ii}{\mathrm{i}}
\newcommand{\bv}{\bm{v}}
\newcommand{\rin}{r_\mathrm{in}}
\newcommand{\rout}{r_\mathrm{out}}
\newcommand{\ciso}{c_\mathrm{iso}}
\newcommand{\tbeta}{\tilde{\beta}}
\newcommand{\teta}{\tilde{\eta}}
\newcommand{\tcool}{t_\mathrm{cool}}
\DeclareMathOperator{\erf}{erf}

\title[Gaps in non-isothermal discs]{Gap formation and stability in 
  non-isothermal protoplanetary discs}

\author[Les and Lin]{Robert Les
  $^1$\thanks{robert.les@mail.utoronto.ca} and Min-Kai Lin $^1$
  \thanks{ mklin924@cita.utoronto.ca} \\ 
$^1$Canadian Institute for Theoretical Astrophysics,  
60 St. George Street, Toronto, ON, M5S 3H8, Canada \\
}

@@

\maketitle
\begin{abstract}
%Hydrodynamic simulations of self-gravitating disc-planet interactions are presented. 
Several observations of transition discs show lopsided
dust-distributions, which is suggestive of a dust-trapping mechanism at work. A
popular explanation is the formation of a large-scale vortex at the
edge of a gap opened by a giant planet. While theoretical models
support this picture, numerical simluations have thus far
employed locally isothermal discs. On the other hand, the theory of the
vortex-forming instability was originally developed for adiabatic
discs. We generalise the study of planetary gap stability to non-isothermal
discs using customised numerical simulations of disc-planet
systems. We include in the energy equation a cooling term with cooling
timescale $t_\mathrm{cool}=\beta\Omega_k^{-1}$, where $\Omega_k$ is
the Keplerian frequency, and examine the effect of $\beta$ on the
stability of gap edges.

%The simulations are customized to examine the stability of gaps opened by massive planets as a function of $\beta$.

### 2014-07-27 paper/results.tex
updated paper

\section{Gaps in low mass discs (RL)}

@@

@@

\begin{figure}
   \includegraphics[scale=.42]{figures/stability_vis6betalow.ps}
   \caption{Same as Fig. \ref{stability_vis9lowb} but $\hat{\nu}=10^{-6}$ and $\tilde{\beta}=0.1$. }
 \label{stability_vis6lowb)}
 \end{figure}

\begin{figure}
   \includegraphics[scale=.42]{figures/stability_vis6betamed.ps}
   \caption{Same as Fig. \ref{stability_vis9lowb} but $\hat{\nu}=10^{-6}$ and $\tilde{\beta}=1.0$. }
 \label{stability_vis6medb)}
 \end{figure}
Same as \ref{stability_vis9lowb} but $\hat{\nu}=10^{-6}$ and $\tilde{\beta}=1.0$. 
\begin{figure}
   \includegraphics[scale=.60]{figures/analysis_sigma50lowb.ps}
   \caption{Density pertibation of disk at time=$50t_p$ with $\hat{\nu}=10^{-9}$ and $\tilde{\beta}=0.1$. }
 \label{shortterm_lowb)}
 \end{figure}

>>>>

\section{Numerical linear stability simulations}
We first consider the effect of a cooling time on the \emph{linear} stability
of planetary gaps. There are two competing effects. Increasing
$t_\mathrm{cool}$ leads to more heating and hence a larger sound-speed
$c_s$, which favours instability \citep{li00} since the vortex
instability is pressre-driven. However, gap-opening requires $r_h>H$,
so increasing the sound-speed, and hence $H$, leads to a shallower
gap (see below) and expected to be more stable.

In the following simulations, the planet is introduced at $t=20P_0$ and
its potential switched on over $10P_0$. At $t=30P_0$ we switch off the
planet potential and azimuthally average the surface density, energy
and velocity fields. We then perturb the density field and continue
evolve the disc. %more details on perturbation: m=1 to 10, amplitude?  
%resolution?
%switch off at t=30 because in full disk-planet sims, instability sets
%in soon after planet introduced

\subsection{Gap structure}
{\bf plots of the gap structure before instability sets in, e.g. at
  t=30. surface density perturbation, gen. vortensity perturbation,
  aspect-ratio. compare diff. beta. gaps become more shallow with
  increasing cooling time (but not significantly - not enough time for
  full gap formation). generalized vortensity: extrema smoothed out
  with increasing cooling - expect more stability. aspect-ratio:
  significant heating. increase in H so expect larger vortices
}

\subsection{Linear modes and growth rates}
{\bf present `planet-off' simulations. one `fourier mode v.s. time'
  plot to show growth of linear instability. 
  compare growth rate and dominant
  m as function of beta (table). 2D figs to contrast (also used to
  show it's the minimum in generalized pv that goes unstable.    
  result: increasing cooling time makes the gap
  more stable, and favors lower m. note: the `basic state' should be
  the system at t=30 after azimuthal average. linear results should
  have small perturbations. 
}

@@

\section{Non-linear evolution of
  gap-edge vortices with finite cooling time} 
{\bf main fig: vortex amplitude v.s. time for diff beta. enough data
  to plot vortex lifetime v.s. beta? table: 
  averaged quantities over quasi-steady state: aspect-ratio (to
  compare with fu at al), rossby number (vortex strength
  v.s. cooling?), maybe alpha visc. vortex size: visible difference?  
  only inviscid cases. describe evolution of one case. main
  conclusion: longer vortex lifetime with increasing cooling time (up
  to some optimal timescale). vortex death: induced-shock and/or
  smoothing the gap edge. describe simulation setup, resolution?
  should mention that results consistent with lower-resolution prelim
  runs. maybe torques? 
}

@@

%\begin{figure}
%   \includegraphics[scale=.42]{figures/stability_vis6betalow.ps}
%   \caption{Same as Fig. \ref{stability_vis9lowb} but $\hat{\nu}=10^{-6}$ and $\tilde{\beta}=0.1$. }
% \label{stability_vis6lowb)}
% \end{figure}

%\begin{figure}
%   \includegraphics[scale=.42]{figures/stability_vis6betamed.ps}
%   \caption{Same as Fig. \ref{stability_vis9lowb} but $\hat{\nu}=10^{-6}$ and $\tilde{\beta}=1.0$. }
% \label{stability_vis6medb)}
% \end{figure}
%Same as \ref{stability_vis9lowb} but $\hat{\nu}=10^{-6}$ and $\tilde{\beta}=1.0$.

\begin{figure}
   \includegraphics[scale=.60]{figures/analysis_sigma50lowb.ps}
   \caption{Density pertibation of disk at time=$50t_p$ with $\hat{\nu}=10^{-9}$ and $\tilde{\beta}=0.1$. }
 \label{shortterm_lowb)}
 \end{figure}
